\textbf{EECS 340: Assignment 5}

### 2020-04-07 assignment_5/article.tex
✨ Add Problem 1(b) responses.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(a)}

@@

>>>>

I did \textbf{(ii)} and \textbf{(vi)} on \textbf{Problem 1(a)}.
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(a)}

@@

\paragraph{(i)} Determine the last coin $c_{\text{last}}$ which will be added to the change set $\{c_1, c_2, c_3, ..., c_{\text{last}-1}\}$. Where the sum of elements of such set plus $c_{\text{last}}$ should be equal to $t$.

\begin{itemize}
    \item Subproblem: $f(v)$ provides the minimum number of coins to make change for $v$, given $n$ types of coin denominations are available. There must be  $v \in [0, t]$ and $v$ must be equal to the sum of some coins from the given $n$ types of coin denominations, to represent a value that is achievable by given coins.
    \item Overall problem: $f(t)$ provides the minimum number of coins to make change for $t$, given $n$ types of coin denominations are available.
\end{itemize}

Let $n_c$ be a type of coin from the provided $n$ types of coins, which means $n_c$ can potentially hold $n$ types of values. We will try all $n_c$(s) as we don't know which coin to use for the $c_1$.

\begin{equation}
    f(v) =
    \begin{cases}
        0 & \text{if \ } v = 0 \\
        min\{f(v - n_c) + 1\} & \text{if \ } v > 0 \\
    \end{cases}\nonumber
\end{equation}

We have $T(n) = \Theta(nt)$. There are $\Theta(t)$ subproblems, as we can divide at most $t$ groups of coin(s) for a total value of $t$ (as for all coins being value $1$), and for each group there are at most $n$ possible choices to iterate (thus $\Theta(n)$). Each choice takes $\Theta(1)$ to execute. \\
$\Longrightarrow T(n) =  \Theta(t) \cdot \Theta(n) \cdot \Theta(1) =  \Theta(nt)$
